\addcontentsline{toc}{chapter}{Abstract}
\begin{abstract}
\thispagestyle{plain}
\setcounter{page}{2}
Global trends indicate that the number of people across the world using the internet has grown to 4.54 billion, an increase of 7 percent (298 million new users) from January 2019 to January 2020. In addition, there are 3.80 billion social media users in January 2020, with this number increasing by more than 9 percent (321 million new users) since same month last year. Globally, more than 5.19 billion people now use mobile phones, with user numbers up by 124 million (2.4 percent) over the past year.
% \footnote{https://datareportal.com/reports/digital-2020-global-digital-overview}

The impact of the aforementioned trends boosted the growth of another industry, the digital platforms. A digital platform can be defined as “a building block that provides an essential function to a technological system and serves as a foundation upon which complementary products, technologies, or services can be developed".
% \cite{digital_platform_def}

Enterprises that have leveraged the affordances of digital platforms have achieved significant growth in size and scale. For instance, digital platform providers in the areas of e-commerce and software development have attained more than \$700 billion in market value. In addition the rise of digital platforms has transformed the landscape of multiple industries such as transportation (e.g., Uber, Grab), hospitality (e.g., Airbnb, CouchSurfing), and software development (e.g., Apple iOS, Google android).
% \cite{digital_platform_number}

%Throughout this report we will firstly define the purpose of digital platforms,then we briefly discuss typologies of digital platforms for the purpose of classifying the digital platform we are trying to make throughout this report.

This report summarises the process of designing a digital platform in hospitality sector from a software engineering perspective. In the first chapter we briefly discuss definition of digital platforms and typologies of such platforms for the purpose of providing some context about the software project we are trying to build. 

Since this project is a summary of an internship stage body of work, we will discuss thoroughly design and development phases of the project as well as methodologies and technologies which are necessary to develop a digital platform such as our project.
\end{abstract}
