\chapter{Conclusion and future work}
\label{chapter6}
\thispagestyle{plain}
Throughout this Report we discussed how to design a booking platform web application from a software engineering point of view. We discussed frameworks used inside Software companies in order to manage a group of software developers working on various parts of the software. After that we have seen dominant architecture for designing Web Applications and how different frameworks incorporate that architecture in order to make the code resusable and more efficient, as well as a logical separation between different parts of the code.
Some of guidelines which were used during the development process came directly from User Experience research which we have included as part of this report. In addition we had to design a secure website therefore the usage of commonly tested platforms such as Spring and ExtJS helped us achieve that goal.
Although this report summarizes the main aspects of developing a software solution from scratch, we had to sacrifice some details and technical perspectives which were not related to the main topic of this paper. One area that seems fruitful for further research and development is usage of Mobile Development platforms in order to further extend the availability and accessibility of the application, since websites by nature run on browsers and 
mobile platforms provide more robust tools for user interaction which leads to creation of a superior user experience.
Another area which requires further studying is the usage of cross platform frameworks for development of digital platforms. These cross platform frameworks reduce the development workload by providing ready to use modules which work across variety of devices. In recent years \textit{Google} and \textit{Facebook} created their own cross platform development frameworks in form of \textit{Facebook REACT} and \textit{Google Flutter}. Considering the attractive nature of these frameworks for developers, the impact of such frameworks on digital platform development requires additional research.